### 2019-05-07 README.Rmd
updated readme

Alternatively the analysis environment can be accessed via [binder](https://mybinder.org/v2/gh/seabbs/DirectEffBCGPolicyChange/master?urlpath=rstudio).

# Docker

This packge was developed in a docker container based on the tidyverse docker image. To run the docker image run:

```{bash, eval = FALSE}
docker run -d -p 8787:8787 --name assessbcgpolicychange -e USER=seabbs -e PASSWORD=seabbs seabbs/assessbcgpolicychange
```

The rstudio client can be found on port :8787 at your local machines ip. The default username:password is seabbs:seabbs, set the user with -e USER=username, and the password with - e PASSWORD=newpasswordhere. The default is to save the analysis files into the user directory.

>>>>

Alternatively the analysis environment can be accessed via [binder](https://mybinder.org/v2/gh/seabbs/AssessBCGPolicyChange/master?urlpath=rstudio).
